%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% One Page Resume
% Version 1.0 (14/10/19)
%
% Original author:
% Evan Krul
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.5in,top=0.5in,right=0.5in,bottom=0.5in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Evan Krul}
\address{Contact: +1 (587) 257-9730 - evan@krul.ca}
\address{LinkedIn: \url{krul.ca}}

\begin{document}

%   EDUCATION   %
\begin{Entry}{Education}
{\bf University of Calgary, Schulich School of Engineering
} \hfill {\bf September 2017 - April 2022}
\\{\em Bsc. Software Engineering}
% \\ Activities and Societies: RoboGals, Eco-Car Team, Leadership Program Member
\end{Entry}


%	TECHNICAL STRENGTHS SECTION

\begin{Entry}{Technical Strengths}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Development languages and tools \ & Java, C#, C++, PHP, HTML, CSS, JavaScript, MySQL \\
Frameworks and CMS \ & Angular, Vaadin, Laravel, Wordpress \\
DevOps \ & Docker, Jenkins, AWS, Google Cloud \\
APIs and Services \ & Custom REST API, ELK Stack, Easy-Post, Stripe
\end{tabular}
\end{Entry}

%	ADDITIONAL STRENGTHS SECTION

\begin{Entry}{Additional Strengths}

\begin{flushleft}
Ability to work in a high-pressure environment, Client Relations, Communication, Leadership\\
Problem Solving, Teamwork, Time management, Written communication on work performed\\
\end{flushleft}
\end{Entry}

%  WORK EXPERIENCE   %
\begin{Entry}{Experience}
{\bf Software Lead} \hfill {\bf September 2019 - Present}
\\{\em Eco Car, Schulich School of Engineering, University of Calgary, Calgary, Alberta}
\begin{itemize} \itemsep -5pt
  \item Coordinate software systems for the team’s Eco Car.
\end{itemize}

{\bf Junior Implementation Developer} \hfill {\bf May 2019 - August 2019}
\\{\em Aimsio, Calgary, Alberta}
\begin{itemize} \itemsep -5pt
  \item Developed Java code and accompanying unit tests to extend the functionalities of the core product. 
  \item Managed client projects by researching and documenting specific user workflows, then developed custom JavaScript/HTML/CSS code within the constraints of the product to extend the functionalities of the product to match client workflows. 
  \item Supported over 30  existing clients (small to medium-sized businesses) by responding to customer support inquiries.
  \item Clear documentation of work performed.
\end{itemize}

{\bf IT Director} \hfill {\bf September 2018 - May 2019}
\\{\em The Engineering Students' Society at the University of Calgary, Calgary, Alberta}
\begin{itemize} \itemsep -5pt
    \item Updated and maintained the society's website (essucalgary.com) throughout the year. 
    \item Implemented an e-commerce system for event ticket sales using the Google API client.
    \item Built functionality that allowed existing members of ESS to receive a discount at checkout by syncing to an existing Google Sheet.
\end{itemize}

{\bf Software Developer} \hfill {\bf June 2015 - July 2017}
\\{\em Global Autobody Supplies, Lethbridge, Alberta}
\begin{itemize} \itemsep -5pt
    \item Designed and developed an e-commerce site. Both the front and back end were implemented with the Laravel framework. 
\end{itemize}

{\bf Software Developer} \hfill {\bf March 2017 - July 2017}
\\{\em Wahid Auto, Lethbridge, Alberta}
\begin{itemize} \itemsep -5pt
    \item Designed and developed a car sales website with an inventory listing. 
\end{itemize}
\clearpage
{\bf Software Developer} \hfill {\bf June 2015 - July 2017}
\\{\em Nuvex Solutions, Lethbridge, Alberta}
\begin{itemize} \itemsep -5pt
    \item Developed various websites for clients in a team environment.
    \item Implementations of the sites varied by case, however, most sites consisted of converting a given design file to HTML, CSS, and JavaScript and implementing a CMS backend.
    \item Implemented specific workflows in PHP.
\end{itemize}
\end{Entry}


%  Additional WORK EXPERIENCE   %
\begin{Entry}{Additional Experience}

{\bf VP Academic} \hfill {\bf April 2019 - Present}
\\{\em Electrical, Computer, and Software Engineering Students' Society at the University of Calgary, Calgary, Alberta}
\begin{itemize} \itemsep -5pt
    \item Student representative at the Department Undergraduate Studies Committee. 
    \item Organize a technical elective information night for students to be introduced to the courses by the professors offering them.
\end{itemize}

{\bf Kitchen Utility Worker, Prep Cook, and Porter} \hfill {\bf February 2016 - March 2019}
\\{\em The View at Lethbridge Retirement Home, Lethbridge, Alberta}
\begin{itemize} \itemsep -5pt
    \item Dishwasher and Prep Cook.
    \item Took initiative to be a porter (evening manager) as required. 
    \item Maintained building and accommodated residents as required.
\end{itemize}

{\bf General Laborer} \hfill {\bf May 2018 - August 2018}
\\{\em Neuman Construction, Lethbridge, Alberta}
\begin{itemize} \itemsep -5pt
    \item General labourer for a construction company mainly focused on renovations and restorations.
\end{itemize}
\end{Entry}

%   SELECT PROJECTS   %
\begin{Entry}{Select Projects \& Achievements}
{\bf BreadEx } \hfill {\bf November 2019}
\\{\em 1\textsuperscript{st} place, Sr. Programming. Schulich Engineering Competition}
\\ A shipping logistics scheduler software. Built with a python distribution scheduler and a front end website implemented with Vaadin and MySQL.

{\bf ScrapCycle} \hfill {\bf November 2019}
\\{\em 2\textsuperscript{nd} place, Code the Change YYC Hackathon }
\\ A material exchange system for corporations. The platform allowed businesses to advertise excess raw
materials on the system. This reduces business waste. Used the Vaadin framework.


{\bf WeaselBeagle} \hfill {\bf September 2019 - December 2019}
\\ A project for a database design class using the {\em MEAN} stack. Pet adoption application that allows shelters to upload animals waiting placements. Adopters can search potential pets and initiate the adoption process. 

{\bf Rental Property Management System} \hfill {\bf November 2019 - December 2019}
\\ A project for a software design class. Online rental property management system that allows landlords to upload properties to the system. Renters can browse the listings and contact the landlords. Used Vaadin and MySQL, deployed on Google Cloud. The project was focused on implementing software design patterns.

{\bf Client-server Toolshop Application} \hfill {\bf May 2019 - June 2019}
\\ Toolshop application utilizing object-oriented design, client-server architecture, multi-threading, JDBC, and Swing GUI.
\end{Entry}


\end{document}
